%-------------------------
% Resume in Latex
% Author: Bruno Stefoni
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & {\footnotesize{#4}} \\
        {{#2}} &  \footnotesize{#3}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Bruno Stefoni}
\newcommand{\phone}{+1 646 203 7124}
\newcommand{\emaila}{brunostefoni12@gmail.com}

\begin{document}
\fontfamily{cmr}\selectfont

%----------HEADING-----------------
{
\begin{tabularx}{\linewidth}{L}
  \textbf{\LARGE \name} \\
  \vspace{1pt}
  New York, NY | \emaila\ | \phone \, |
    \href{https://www.linkedin.com/in/bruno-stefoni-escudero/}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {LinkedIn}} |
  \href{https://github.com/BrunoSE}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {GitHub}} |
  \href{https://scholar.google.com/citations?user=clOK1mEAAAAJ}{\raisebox{0.0\height}{\footnotesize \faGraduationCap}\ {Scholar}}
  

\end{tabularx}
}
\vspace{-0.6cm} % Adjust this value as needed


%-----------PROFESSIONAL SUMMARY-----------
\section{\textbf{Professional Summary}}
\vspace{0.1cm}
Seven years of experience with AI, Machine Learning and Data: leading projects to deploy AI and ML solutions to the cloud; building data pipelines to train models; designing A/B tests and tracking KPIs.

%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {CloudWerx}{Senior AI / ML Engineer}
      {Manhattan, New York}{Nov 2023 – Present}
      \resumeItemListStart
        \item {Leading multiple customer projects, deploying ML and AI solutions using GCP, Vertex AI, Vertex Search, Agent Builder, Big Query ML, Kubeflow, LLMs, Stable Diffusion, etc.}
        \item {Example projects: custom OSS LLM RAG chatbot implementation, Augmented Search using RAG and Gemini, fine-tuning pipeline for diffusion model, MLOps Kubeflow pipeline for model CI/CD.}
        \item {Example customer industries: cyber security, ecommerce, finance, design, advertising, robotics, real estate, data.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Aetna - CVS Health}{Data Scientist}
      {Manhattan, New York}{Sep 2023 – Oct 2023}
      \resumeItemListStart
        \item {Designed A/B test experiment with 9 MM MAU App to measure campaign impact on customer adoption KPIs.}
        \item {Analyzed data in GCP Big Query to perform demographic analysis for a live A/A experiment.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Sortile}{Data Scientist}
      {Manhattan, New York}{Jun 2023 – Aug 2023}
      \resumeItemListStart
        \item {Built a 92\% accurate XGBoost classifier to identify black/white fibers using light wavelength sensor data.}
        \item {Developed and benchmarked XGBoost, LGBM and Deep Learning models. Deployed XGB model on AWS Lambda.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Google}{Data Scientist Intern}
      {Mountain View, California}{Jun 2022 – Aug 2022}
      \resumeItemListStart
        \item {Conducted detailed market research and graph analysis by building a network dataset from diverse data sources using PLX, BigQuery and Python.}
        \item {Detected up to 15\% of user churn by continuous survival and time series analysis of Software adoption rate data.}
        \item {Presented insights to internal stakeholders and management. Proposed a new methodology for analysts.}
      \resumeItemListEnd
      
    \resumeSubheading
      {STP}{Data Scientist}
      {Santiago, Chile}{May 2018 – May 2022}
      \resumeItemListStart
        \item {Built and implemented a company-wide chat bot on prem cloud server to support management and on-site workers.}
        \item {Drove STP's revenue by identifying routes with up to 25\% difference between planned and real bus speeds.}
        \item {Prevented \$500K investment on less accurate tech by launching a statistical study.}
        \item {Detected data outliers due to faulty batteries in 20\% of STP's electric fleet via statistical analysis.}
        \item {Increased main contract KPI by 6\% by scraping Twitter data to alert service disruptions.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


\vspace{-0.5cm} % Adjust this value as needed

%-----------PROJECTS AND PUBLICATIONS-----------------
\section{\textbf{Projects and Publications}}
\resumeSubHeadingListStart
  \resumePOR{Anky}{Developed RAG + SFT/DPO fine tuned LLM with llama.cpp using social network data }{}
  \resumePOR{S\&P Global Capstone Project}{News classification by fine-tuning BERT from unlabeled data (97\% accuracy)}{}
  \resumePOR{Master's Thesis Publications}{Two papers published on computer microscopic simulation}{}
  \resumePOR{Deep Learning Competition}{Next frame video prediction using Transformer and CNN (ResNet) in JEPA network}{}
  \resumePOR{Text Topic Analysis}{LDA and GloVe word embeddings on large academic thesis corpus}{}
  \resumePOR{Twitter Sentiment Analysis}{Using fastText and fine-tuning BERT for content strategy assessment}{}
  \resumePOR{Hackathon Winner}{Led team of 6, designed and developed an app for transit users}{}
\resumeSubHeadingListEnd

\vspace{-0.2cm} % Adjust this value as needed

%-----------EDUCATION-----------------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {NEW YORK UNIVERSITY}{Master of Science in Data Science}
      {GPA: 3.8/4.0}{2021 – 2023}
      \resumeItemListStart
        \item {Coursework: Deep Learning, Machine Learning, Big Data, Optimization \& Linear Algebra, Probability \& Statistics}
        \item {TA of Data Science Class at NYU Business School for two semesters}
      \resumeItemListEnd
      
% Force a page break here
\clearpage
. \vspace{0.4cm}
    \resumeSubheading
      {UNIVERSIDAD DE CHILE}{Bachelor and Master's degree in Engineering}
      {Final grade 6.6/7.0}{2018}
      \resumeItemListStart
        \item {Graduated with highest distinction in top 10\% GPA of cohort}
        \item {Granted Outstanding Student Award}
        \item {TA of five different courses, e.g., Stochastic Processes, Network Optimization}
        \item {Key Modules: Data Mining, Computer Science I and II, Probability, Statistics, Optimization, Operations Research}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-0.3cm}

%-----------SKILLS-----------------
\section{\textbf{Skills}}
 \begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
    \textbf{Certifications:} Google Professional Machine Learning Engineer \\
     \textbf{Programming Languages:} Python, R, MATLAB, Java \\
     \textbf{AI Libraries:} Transformers, Langchain, OpenAI API, Anthropic API, Instructor, Pydantic, HuggingFace \\
     \textbf{ML Libraries:} PyTorch, PyTorch-Lightning, XGBoost, LGBM, scikit-learn, statsmodels \\
     \textbf{Cloud Platforms:} Google Cloud Platform (GCP), AWS \\
     \textbf{Databases:} SQL (SQlite), PostgreSQL (AlloyDB), BigQuery, Vector DBs (Milvus, Pinecone) \\
     \textbf{DevOps:} Git, Docker, Terraform, Bash, Linux \\
     \textbf{Data Analysis:} Pandas, NumPy, Plotly, Seaborn, Matplotlib \\
     \textbf{NLP:} NLTK, SpaCy, fastText \\
     \textbf{Big Data:} pySpark, Dask, Dataflow, Apache Beam \\
     \textbf{Languages:} Native English and Spanish speaker, Intermediate Italian
    }}
 \end{itemize}

\end{document}
